LAGOS lake depth

### 2019-09-23 lagos_depth.Rmd
use merged dataset over lagosne

knitr::opts_chunk$set(echo = FALSE, timeit = TRUE)
```

```{r data, message=FALSE, echo=FALSE}
library(LAGOSNE)
library(ggplot2)
library(sf)
library(dplyr)
library(cowplot)
library(ggforce)

lg       <- lagosne_load("1.087.1")
lg_depth <- dplyr::select(lg$lakes_limno, 
                          lagoslakeid, maxdepth, maxdepthsource) %>% 
  mutate(color = cut(maxdepth, 
                     round(quantile(maxdepth, c(0, 0.05, 0.5, 0.95, 1), 
                                    na.rm = TRUE)))) %>% 
  left_join(lg$locus, by = "lagoslakeid") %>%
  mutate(has_limno = lagoslakeid %in% lg$epi_nutr$lagoslakeid) %>%
  # dplyr::filter(!is.na(maxdepth)) %>%
  coordinatize()
```

>>>>

knitr::opts_chunk$set(echo = FALSE, timeit = TRUE, eval = FALSE)
source("scripts/99_utils.R")
```

```{r data, message=FALSE, echo=FALSE, eval=TRUE}
dt <- read.csv("data/lagosus_depth.csv", stringsAsFactors = FALSE) %>%
  mutate(maxdepth_class = cut(max_depth_m, 
                     round(quantile(max_depth_m, c(0, 0.05, 0.5, 0.95, 1), 
                                    na.rm = TRUE)))) %>% 
  coordinatize(latname = "lat", longname = "long")
```

 * Number of lakes w/ max depth by state

 * Fraction of lakes w/ max depth by state

 * Ridgeline plot of lake depth
